### 2020-04-12 Thesis-Chapter1-Introduction.tex
Incorporate feedback from Jesse
https://github.com/Jesse-Millwood -- Thanks!

Difficult policy matters are \acp{wicked-prob}. Originally coming from the field of design theory, the term
\ac{wicked-prob} uses ``wicked'' not in the moral sense, but in the malignant, vicious, and tricky sense
\cite{rittel_dilemmas_1973}. Unlike their ``tame'' counterparts which science and engineering are well equipped to
answer, \acp{wicked-prob} lack clear formulations, causes, resolutions, or metrics. Each attempt at a solution matters,
has unintended consequences, and often exists in a pattern of chronic policy failure.

\Acl{EA} is a wicked problem. In encryption policy, \ac{EA} is alternative means of decryption intended for law
enforcement use. Characterized by a dynamic technological environment, disagreement about underlying values, and
resistance to a clear solution, the debate on \acl{EA} refuses to end. This paper will not attempt to end the debate,
but to inform it with additional structure.

@@

The conflict at the heart of the encryption and \acl{EA} is that the same cryptographic and design principles that
underlie nearly all digital security also enable an unprecedented degree of individual privacy. Encryption is a
foundational tool to the integrity and confidentiality of all connected computing systems. Its increasing ubiquity in
communications and storage provides clear benefits and should be welcomed by all. In a world where information security
is frightfully poor yet increasingly important, strong encryption's necessity can not be understated. However, the
privacy afforded by certain encryption technologies hampers law enforcement investigations and hides wrongdoing. In a
society that cares about bringing wrongdoers to justice, this risk should not be ignored.

@@

In the long term, increased regulation of the tech industry in general is inevitable, and regulation of encryption is
possible. Despite strong encryption's benefits, regulatory interest in the subject has not subdued. The form that
regulation will take in the field of encryption depends on the good faith efforts made to equitably balance all the
benefits and risks involved in deploying a cryptographic system. If the technical community acts, it can not only be
prepared for regulation, but lead and shape it.

@@

For all these reasons, it is time that the technical community moves the debate forward.

@@

The paper serves to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.-focused history of encryption regulation, technology, and conflict, it introduces argument maps and threat
models using data flow diagrams. In the following chapters it analyzes exceptional access arguments in detail and
creates a multi-level threat model, broken down by the significantly different challenges posed by \acl{DAR} and
\acl{DIM}. The paper concludes with a set of policies and principles to apply to the problem in light of valid arguments
and threats.

>>>>

Difficult policy matters are \acp{wicked-prob}. Originally coming from the field of design theory, the term
``\ac{wicked-prob}'' uses ``wicked'' not in the moral sense, but in the malignant, vicious, and tricky sense
\cite{rittel_dilemmas_1973}. Unlike their ``tame'' counterparts which science and engineering are well equipped to
answer, \acp{wicked-prob} lack clear formulations, causes, resolutions, or metrics. Each attempt at a solution matters,
has unintended consequences, and often exists in a pattern of chronic policy failure.

\Acl{EA} is a wicked problem. In encryption policy, \ac{EA} is alternative means of decryption intended for law
enforcement use. Characterized by a dynamic technological environment, disagreement about underlying values, and
resistance to a clear solution, the debate on \ac{EA} refuses to end. This paper will not attempt to end the debate, but
to inform it with additional structure.

@@

The conflict at the heart of the encryption and \ac{EA} is that the same cryptographic and design principles that
underlie nearly all digital security also enable an unprecedented degree of individual privacy. Encryption is a
foundational tool to the integrity and confidentiality of all connected computing systems. Its increasing ubiquity in
communications and storage provides clear benefits and should be welcomed by all. In a world where information security
is frightfully poor yet increasingly important, strong encryption's necessity can not be understated. However, the
privacy afforded by certain encryption technologies hampers law enforcement investigations and hides wrongdoing. In a
society that cares about bringing wrongdoers to justice, this risk should not be ignored.

@@

In the long term, increased regulation of the tech industry in general is inevitable, and regulation of encryption is
possible. Despite strong encryption's benefits, regulatory interest in the subject has not subdued. The form that
regulation will take in the field of encryption depends on the good faith efforts made to equitably balance all the
benefits and risks involved in deploying a cryptographic system. If the technical community acts, it can lead and shape
legislation instead of being subjected to it.

@@

For these reasons, it is time that the technical community moves the debate forward.

@@

This paper serves to clarify the arguments composing debate and the nature of the technical problem. After reproducing a
brief U.S.-focused history of encryption regulation, technology, and conflict, it introduces argument maps and threat
models using data flow diagrams. In the following chapters it analyzes exceptional access arguments in detail and
creates a multi-level threat model, broken down by the significantly different challenges posed by \acl{DAR} and
\acl{DIM}. The paper concludes with a set of policies and principles to apply to the problem in light of valid arguments
and threats.

### 2020-04-12 Thesis-Chapter2-Background.tex
Incorporate feedback from Jesse
https://github.com/Jesse-Millwood -- Thanks!

The problem of strong encryption and exceptional access exists in a technical, historical, and regulatory context. This
chapter introduces cryptography, summarizes the history of encryption and the crypto wars, lists relevant encryption
regulations, and lists prominent technical \ac{EA} proposals. It then introduces argument maps as a logical modeling
tool, and introduces threat modeling with data flow diagrams.

@@

\Ac{cryptography} is the study of techniques for communicating secretly in the presence of third parties. This is
performed by using some \ac{cipher} to translate between \ac{plaintext} and \ac{ciphertext}. The cipher is the tool or
algorithm that performs the translation, plaintext is the original data, and ciphertext is the encoded data. The
processes for translating from plaintext to ciphertext and back are \ac{encryption} and \ac{decryption}. A well-designed
cipher ensures that only those with the correct secret information, the \ac{key}, can perform encryption or decryption
on the text.

@@

All these realities--government discomfort with absolute privacy, rapidly increasing availability of strong encryption,
and a blossoming computer industry foundationally reliant on cryptography--came to a head in what has become known as
\ac{the-cw1}.

@@

The following sections summarize the encryption regulatory environment and technical approaches to exceptional access.

@@

In order to advance the \ac{EA} debate, it helps to organize the all the arguments used in a cohesive manner. One way to
organize arguments is to create argument maps. Argument maps are graphical representations of the logical structures and
relationships between statements, premises, and conclusions. Argument maps are an outgrowth of the same research by
Horst Rittel that originated the idea of \acp{wicked-prob}. In 1970 his research group developed \acp{IBIS} to break
down \acp{wicked-prob} and document the reasoned approach that goes into solving them \cite{kunz_issues_1970}. Interest
in \ac{IBIS} has waxed and waned. Some software tools have been developed, including the now-defunct gIBIS
\cite{conklin_gibis_1988} and Compendium \cite{dutoit_hypermedia_2006} tools designed to produce graphical
representations. Argdown is a recent tool that generates argument maps from structures specified in a Markdown-based
language \cite{voigt_argdown_2018}.

>>>>

The problem of strong encryption and \acl{EA} exists in a technical, historical, and regulatory context. This chapter
introduces cryptography, summarizes the history of encryption and the ``crypto wars,'' lists relevant encryption
regulations, and lists prominent technical \ac{EA} proposals. It then introduces argument maps as a logical modeling
tool, and introduces threat modeling with data flow diagrams.

@@

\Ac{cryptography} is the study of techniques for communicating secretly in the presence of third parties. This is
performed by using some \ac{cipher} to translate between \ac{plaintext} and \ac{ciphertext}. The cipher is the tool or
algorithm that performs the translation, plaintext is the original data, and ciphertext is the encoded data. The
processes for translating from plaintext to ciphertext and back are \ac{encryption} and \ac{decryption}. A well-designed
cipher ensures that only those parties with the correct secret information, the \ac{key}, can perform encryption or
decryption on the text.

@@

All these realities--government discomfort with absolute privacy, rapidly increasing availability of strong encryption,
and a blossoming computer industry foundationally reliant on cryptography--came to a head in what has become known as
the first ``crypto war.''
% \ac{the-cw1}.

@@

The following sections summarize the encryption regulatory environment and technical approaches to \ac{EA}.

@@

In order to advance the \ac{EA} debate, it helps to organize all the arguments used in a cohesive manner. One way to
organize arguments is to create argument maps. Argument maps are graphical representations of the logical structures and
relationships between statements, premises, and conclusions. Argument maps are an outgrowth of the same research by
Horst Rittel that originated the idea of \acp{wicked-prob}. In 1970 his research group developed \acp{IBIS} to break
down \acp{wicked-prob} and document the reasoned approach that goes into solving them \cite{kunz_issues_1970}. Interest
in \ac{IBIS} has waxed and waned. Some software tools have been developed, including the now-defunct gIBIS
\cite{conklin_gibis_1988} and Compendium \cite{dutoit_hypermedia_2006} tools designed to produce graphical
representations. Argdown is a recent tool that generates argument maps from structures specified in a Markdown-based
language \cite{voigt_argdown_2018}.
